	dtkintegrate wf?name [option [value(s)]] ... [option [value(s)]]

Where wf?name is the input wfx(wfn) name, and options can be:
Where wf?name is the input wfx(wfn) name, and options can be:

  -p prop   	Choose the property to be integrated. prop is a character,
            	  which can be (d is the default value):
         		d (Electron Density --Rho--)
         		m (Electron Density --tildeRho-- in Momentum Space)
         		l (Laplacian of Electron Density)
         		E (Electron Localization Function --ELF--)
         		S (Shannon-Entropy Density)
         		T (Shannon-Entropy Density in Momentum Space)
         		g (Magnitude of the Gradient of the Electron Density)
         		L (Localized Orbital Locator --LOL--)
         		G (Kinetic Energy Density G)
         		K (Kinetic Energy Density K)
         		e (Ellipticity)
         		k (Kinetic Energy Density K in Momentum Space)
         		M (Magnitude of the Gradrient of LOL)
         		V (Molecular Electrostatic Potential)
         		P (Magnitude of Localized Electrons Detector)
         		s (Reduced Density Gradient --s--)
         		r (Region of Slow Electrons --RoSE--)
         		v (Virial Potential Energy Density)
         		D (Density Overlap Regions Indicator --DORI--)
         		b (Spin density)
         		q (One electron disequilibrium --Rho squared--)
         		Q (One electron disequilibrium in momentum space --tildeRho squared--)
         		u (Scalar Custom Field)
  -b L U    	Set the integration domain to be a cube, whose
            	  left,lower,back corner is (L,L,L) and right,upper,front corner
            	  is (U,U,U). Setting L=U=0 instruct the program to
            	  set the boundaries automatically.
  -i t      	Set the integrator type to be t. Here, t is a char of the following list:
            		v Vegas-Monte Carlo
            		m Miser-Monte Carlo
            		s Gauss-Legendre-Spherical-t design cubature.
            		    Warning: this only works for single atoms when the field's
            		    domain is real space, or for any molecule if the field's
            		    domain is momentum space.
  -J        	Setup alpha- and beta-spin density matrices.
  -o outname 	Set the output file name.
             	  (If not given, the program will create one out of
             	  the input name; if given, the gnp file and the pdf will
             	  use this name as well --but different extension--).
  -V         	Display the version of this program.
  -h         	Display the help menu.

  --help    		Same as -h
  --version 		Same as -V
--------------------------------------------------------------------------------
               Specific options for Vegas-Monte Carlo integrator.
--------------------------------------------------------------------------------
  --vegas-interv  N  	Set the number of intervals to be N. N is the number of
                     	  subregions (intervals) to which the original domain is
                     	  divided. Default: N=10.
  --vegas-npts NMCP  	Set the number of MC-points to sample per iteration
                     	  to be NMCP. Default: NMCP=10,000.
  --vegas-iter I     	Set the maximum number of iterations to be I.
                     	  Default: I=20.
  --vegas-conv-rat A 	Set the damping parameter to be A.
                     	  Default: A=1.0.
  --vegas-therm T    	Set the first T iterations to be ignored for computing
                     	  the expected integral. Default value: T=0.
  --vegas-tol tol    	Set the tolerance for considering an optimal grid to be
                     	  tol. Default value: tol=0.0.
  --vegas-stop-ref X 	Set the num. of iterations where the grid will be
                     	  refined. Usually, X is not defined.
  --vegas-searchmax N	Use N sample points to find the global maximum of prop.
                     	  This option is applied only momentum space functions.
                     	  Default: N=1,000,000.
--------------------------------------------------------------------------------
               Specific options for Miser-Monte Carlo integrator.
--------------------------------------------------------------------------------
  --miser-npts NMCP  	Set the number of MC-points to sample per iteration
                     	  to be NMCP. Default: NMCP=500,000.
  --miser-dith d     	Set dith=d. Default: d=0.05.
--------------------------------------------------------------------------------
      Specific options for Gauss-Legendre-Spherical-t Cubature integrator.
--------------------------------------------------------------------------------
  --lsptd-ol OGL     	Use OLG order for the Gauss-Legendre terms (radial,
                     	   default: 64).
                     	  Options: 2, ... , 1024
  --lsptd-os OSTD    	Use OSTD order for the Sperical-t design terms (angular,
                     	   default: 21).
                     	  Options: 3,5,7,9,11,13,15,17,19,21,31,39,45,55,63,71,77,89,101,111
--------------------------------------------------------------------------------
                     Specific options for diatomic systems.
--------------------------------------------------------------------------------
         Cubatures for diatomic systems are built using Nr (Na) points
       for the radial (angular) part (see dtkmanual for specific details)
            For 3D integrals, the number of abscissas is (3*Na*Nr).
        For 6D integrals, the number of abscissas is (9*Na*Na*Nr*Nr/16).
        Since the most expensive computation is related to 6D integrals,
           In this version, only Nr and Na can be altered and must be
           even. If an odd number is provided, DTK will guess a close
                                  even number.
  --diatomic-rord Nr 	Use Nr points for the radial part of the cubatures.
                     	  This option applies to diatomic systems, Default: Nr=32.
                     	  Nr is the number of points used for the radial part (see above).
                     	  Options: 2, ... , 1024
  --diatomic-aord Na 	Use Na points for the angular part of the cubatures.
                     	  This option applies to diatomic systems, Default: Na=32.
                     	  Na is the number of points used for the angular part (see above).
                     	  Options: 2, ... , 1024
--------------------------------------------------------------------------------
