	dtkfindcp wf?name [option [value(s)]] ... [option [value(s)]]

Where wf?name is the input wfx(wfn) name, and options can be:
Where wf?name is the input wfx(wfn) name, and options can be:

  -a        	Draw transparent spheres around each nuclei in the wf? file.
  -o outname	Set the output file name (*.log).
            	  (If not given the program will create one out of
            	  the input name; if given, the pov file will
            	  use this name as well --but different extension--).
  -m        	Save the coordinates of atoms, critical points and gradient
            	  paths (if calculated, see option -G) into *dat files.
  -p     	Create a pov file. No image will be generated.
  -P     	Create a png image using povray (calls povray),
         	  deletes pov file.
  -c p   	Set the camera vector direction for the povray scene.
         	  p is an integer which can take the values
         	  001,010,100,101,110,111; the camera will be located
         	  somewhere in the direction (x,y,z), where xyz is one of 
         	  the above values.
  -g     	Draw the bond paths (gradient paths) in the POV file.
  -T     	Set the style for the gradient paths to be tubes.
  -G     	Skip the calculation of the bond gradient paths.
  -k     	Keeps the pov file if option -P is used.
  -t cpt 	Set the type of critical point to be searched. cpt can be 
         	  one of the following fields (Density is the default):
         		d (Density)
         		L (Localized Orbital Locator -LOL-)
  -e     	Perform an extended search of critical points. This
         	  will take some more time, but it could find more CPs
         	  than the simple search.
  -v     	Verbose mode (displays additional information (for example the 
         	  output of povray, etc.
  -V        	Display the version of this program.
  -h		Display the help menu.

  --help    		Same as -h
  --version 		Same as -V
********************************************************************************
  Note that the following programs must be properly installed in your system:
                                     povray
                                 graphicsmagick
                                      gzip
********************************************************************************
