                         :-) Created by: JMSA/JMHP (-:

********************************************************************************


Usage:

	dtknci wf?name [option [value(s)]] ... [option [value(s)]]

Where wf?name is the input wfx(wfn) name, and options can be:
Where wf?name is the input wfx(wfn) name, and options can be:

  -a aG1 aG2	Sets the gnuplot angles to be aG1 and aG2.
            	  Use dtkqdmol to check and set these angles.
  -A aX aY aZ	Sets the view angles to be aX, aY, and aZ.
  -b val    	Sets the color scale to be [-val,val].
  -B vMin vMax	Sets the color scale to be [vMin,vMax].
  -c        	Skips the cube calculation. Notice this will assume that the
            	  cube was previously computed.
  -k        	Keeps the pov-ray script (see also option P, below).
  -l palette	Selects the color scheme 'palette', which can be any of:
            	  bentcoolwarm blues bugn gnbu greens greys inferno
            	  magma moreland oranges orrd plasma pubu purples rdbu
            	  rdylbu rdylgn reds spectral viridis ylgn ylgnbu
            	  ylorbr ylorrd
  -n  dim   	Sets the number of points per direction for the s-cube
            	  to be dim x dim x dim.
  -N nx ny nz	Sets the individual points per direction for the s-cube
            	  to be nx x ny x nz.
  -o outname	Sets the output file names to use 'outname' as a basename,
            	  i.e., the pov and png files will be named:
            	  outnameNCI.pov and outnameNCI.png, respectively.
  -s        	Uses a smart cuboid for the s-cube. The number of points for the
            	  largest direction will be 80.
  -S ln     	Uses a smart cuboid for the s-cube. ln is the number of points
            	  the largest axis will have. The remaining axes will have
            	  a number of points proportional to the molecule dimensions.
  -P        	Generates a pov-ray script and renders it. Notice: this requires
            	   povray to be installed in your system.
  -V        	Displays the version of this program.
  -h		Display the help menu.

  --configure-nci rMin rMax sMax 	Set the parameters rhoMin, rhoMax,
             		  and redDensGradMax to be rMin, rMax, and sMax,
             		  respectively. Default values: rhoMin=0.0005,
             		  rhoMax=0.065, and redGradMax=2.
  --help    		Same as -h
  --version 		Same as -V
